%%%% Proceedings format for most of ACM conferences (with the exceptions listed below) and all ICPS volumes.
\documentclass[sigconf]{acmart}
%%%% As of March 2017, [siggraph] is no longer used. Please use sigconf (above) for SIGGRAPH conferences.

%%%% Proceedings format for SIGPLAN conferences 
% \documentclass[sigplan, anonymous, review]{acmart}

%%%% Proceedings format for SIGCHI conferences
% \documentclass[sigchi, review]{acmart}

%%%% To use the SIGCHI extended abstract template, please visit
% https://www.overleaf.com/read/zzzfqvkmrfzn


\usepackage{booktabs} % For formal tables


% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}


% DOI
\acmDOI{10.475/123_4}

% ISBN
\acmISBN{123-4567-24-567/08/06}

%Conference
\acmConference[CIKM'18]{ACM International Conference on Information and Knowledge Management}{October 2018}{Lingotto, Turin Italy}
\acmYear{1997}
\copyrightyear{2016}


\acmArticle{4}
\acmPrice{15.00}
\newcommand{\FactCheck}{\textsc{FactCheck}}
\newcommand{\DeFacto}{\textsc{DeFacto}}


\begin{document}
\title{	FactCheck: Validating RDF Triples using Textual Evidence}
%\subtitle{Extended Abstract}
%\subtitlenote{The full version of the author's guide is available as
%  \texttt{acmart.pdf} document}


\author{Zafar Habeeb Syed}
\affiliation{%
  \institution{Data Science Group, Paderborn University}
  \city{Paderborn}
  \state{Germany}
}
\email{zsyed@mail.uni-paderborn.de}

\author{Michael R\"oder}
\affiliation{%
  \institution{Data Science Group, Paderborn University}
  \city{Paderborn}
  \state{Germany}
}
\email{michael.roeder@upb.de}

\author{Axel-Cyrille Ngonga Ngomo}
\affiliation{%
  \institution{Data Science Group, Paderborn University}
  \city{Paderborn}
  \state{Germany}
}
\email{axel.ngonga@upb.de}

% The default list of authors is too long for headers.
\renewcommand{\shortauthors}{Zafar Syed et al.}


\begin{abstract}
With the increasing uptake of knowledge graphs in domains as diverse as question answering and geo-spatial information systems comes an increasing need for validated the knowledge contained in these graphs. However, the sheer size and number of knowledge bases used in real-world applications makes manual fact checking impractical. In this paper, we present \FactCheck, an automated fact checking approach. The basic principle behind \FactCheck{} is to detect evidence for input facts from trustworthy source documents. To implement this principle, \FactCheck{} systematically retrieves documents from a given reference corpus and extracts sentence parse trees that can be used to validate the input fact. Based on these documents, \FactCheck{} calculates a truth score. In addition, \FactCheck{} also provides the user the list of documents used to validate the input statement. We evaluated our approach on two different benchmark datasets and two different corpora. Our results show that \FactCheck's outperforms the state of the art by up to 13.3\% in F-measure and 19.3\% AUC. \FactCheck{} is open-source and available at \url{https://github.com/dice-group/FactCheck}.
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below.
%


\ccsdesc[500]{Semantic Web}
\ccsdesc[300]{Natural Language Processing}
\ccsdesc{Information Retrieval}
\ccsdesc[100]{Machine Learning}


\keywords{Fact Checking, Knowledge Graphs, Dependency parsing, Information Extraction}


\maketitle

\input{samplebody-conf}

\bibliographystyle{ACM-Reference-Format}
\bibliography{sample-bibliography}

\end{document}
